Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-03 metrics.tex
Metrics intro done

Once we have defined the coding schemes behavior in terms of encoding
and decoding, we proceed to describe the metrics considered in our study.
We review the energy consumption of the Raspberry Pi since this platform
is deployed at a large scale in scenarios where (i) energy is
constrained to the lifetime of the device battery and (ii) the devices
could be established in locations that are unavailable for regular
maintenance. Typical use cases of this type of scenarios are sensor
applications where devices are positioned for measurement retrieval
without any supervision for large periods fo time. In this type of
settings, both overall and per-bit energy consumption of the devices
during the encoding and decoding process are relevant parameters that
impact in the network performance for a given coding scheme. Also,
Raspberry Pi processors are based in the \ac{ARM} architecture which
is the same as in mobile devices like smartphones or tables.
Therefore, the Raspberry Pi could be used to get an estimate of
computing capabilities of a mobile device that is much more easy-deployable
and at a lower overall cost.

To complement our study, we consider the goodput defined as the ratio
of the useful delivered information at the application layer and the total
delivery time. We focus on the goodput considering only the coding process,
i.e. we assume that the application data has been properly
generated before encoding and also correctly post-processed after decoding.
The goodput is a measure for the effective processing speed since it
excludes protocol overhead but considers all delays related with
algorithmic procedures, field operations, hardware processing,
multicore coordination (where it applies), etc. Moreover, encoding
and decoding goodput permits to observe if coding is a system-block
that limits the end-to-end performance. For example, a low goodput
would affect the \ac{QoE} of delay-densitive applications for the
end user. Use cases of the

>>>>

Once defined the coding schemes behavior in terms of encoding
and decoding, we proceed to describe the metrics considered in our study.
We consider the goodput defined as the ratio of the useful delivered
information at the application layer and the total delivery time. We focus
on the goodput considering only the coding process, i.e. we assume that
the application data has been properly generated before encoding and
also correctly post-processed after decoding. The goodput is a measure
for the effective processing speed since it excludes protocol overhead
but considers all delays related with algorithmic procedures, field
operations, hardware processing, multicore coordination (where it applies),
etc. Moreover, encoding and decoding goodput permits to observe if coding is
a system-block that limits the end-to-end performance. As a reference, a low
goodput would affect the \ac{QoE} of delay-intolerant applications for the
end user. For example, Raspberry Pi processors are based in the \ac{ARM}
architecture which is the same as in mobile devices such as smartphones or
tables. Mobile user applications are typically delay-intolerant.
Therefore, the Raspberry Pi might be used as an experiemental tool to
get an estimate of computing capabilities of a mobile device that is
much more easy-deployable and at a lower overall cost.

To complement our study, we review the energy consumption of the Raspberry
Pi since this platform is deployed at a large scale in scenarios where (i)
energy is constrained to the lifetime of the device battery and (ii) the
devices could be established in locations that are unavailable for
regular maintenance. Typical use cases of this type of scenarios are
sensor applications where devices are positioned for measurement retrieval
without any supervision for large periods fo time. In this type of settings,
both overall and per-bit energy consumption of the devices during the
encoding and decoding process are relevant parameters that impact in the
network performance for a given coding scheme.
